---
title: "week6_lab_coding"
author: "Andrea Gracia"
date: "11/17/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Part 1: Attach packages

In your .Rmd setup chunk, attach the following packages:
Part 1: Attach packages
```{r}
library(tidyverse)
library(palmerpenguins)
library(ggpubr)
library(broom)
```
Part 2: A rank-based test example (Mann Whitney U)
```{r}
set.seed(1414)
gp_1 <- sample.int(20, size=15, replace=TRUE)

set.seed(1424)
gp_2 <- sample.int(30, size=15, replace=TRUE)

hist(gp_1)
hist(gp_2)

my_mwu <- wilcox.test(gp_1, gp_2)
```

Part 3: Simple linear regression
```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point()
```

```{r}
penguin_lm <- lm(body_mass_g ~ flipper_length_mm, data = penguins)
summary(penguin_lm)
penguin_lm_tidy <- broom::tidy(penguin_lm)

# Get the intercept: 
penguin_int <- penguin_lm_tidy$estimate[1]
penguin_int

# Then to get the flipper_length coefficient:
penguin_coef <- penguin_lm_tidy$estimate[2]
penguin_coef

# Metrics at a glance: 
penguin_lm_out <- broom::glance(penguin_lm)
penguin_lm_out

"Simple linear regression was used to explore the relationship between penguin flipper length (mm) and body mass (g) across all three penguin species, and including both male and female penguins. A significant regression model was found ($\beta$ = `r round(penguin_coef,3)`, F(`r penguin_lm_out$df`,`r penguin_lm_out$df.residual`) = `r round(penguin_lm_out$statistic,1)`, p < 0.001) with an R^2^ of `r round(penguin_lm_out$r.squared,3)`."
```
Use the plot() function on the model, which will automatically create four useful visualizations to consider assumptions!

```{r}
plot(penguin_lm)
```

Now that we’ve explore the assumptions and have decided that linear regression is a valid tool to describe the relationship between flipper length and body mass, let’s look at the model.

Use geom_smooth(method = "lm") to add a linear model to an existing scatterplot

Use stat_cor() and/or stat_regline_equation() to add equation information directly to the plot panel, at an x- and y-position that you specify (and yes, you can mess with the digits & appearance here)

```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point(size = 2) +
  geom_smooth(method = "lm",
              color = "red",
              size = 0.5,
              fill = "gray10",
              alpha = 0.5) +
  theme_light() +
  ggpubr::stat_regline_equation(label.x = 180, label.y = 5700)
```
Find Pearson’s r for correlation:
```{r}
penguins_cor <- cor.test(penguins$flipper_length_mm, penguins$body_mass_g)
```

